Clustering time series based on probability distributions across temporal granularities

### 2021-10-31 main.Rmd
gitignore update

With a way to obtain pairwise distances, any clustering algorithm can be employed that supports the given distance metric as input. A good comprehensive list of algorithms can be found in @Xu2015-ja based on traditional ways like partition, hierarchy or more recent approaches like distribution, density and others. We employ agglomerative hierarchical clustering in conjunction with Ward's criteria (XXX reference). Hierarchical cluster techniques fuse neighbouring points sequentially to form bigger clusters, beginning with a full pairwise distance matrix. The distance between clusters is described using a "linkage technique". This agglomerative approach successively merges the pair of clusters with the shortest between-cluster distance using Ward's linkage method. Hierarchical algorithms is one of the most widely used, can operate with data of any form, has reasonable scalability, and the number of clusters is not needed as a parameter.

>>>>

With a way to obtain pairwise distances, any clustering algorithm can be employed that supports the given distance metric as input. A good comprehensive list of algorithms can be found in @Xu2015-ja based on traditional ways like partition, hierarchy or more recent approaches like distribution, density and others. We employ agglomerative hierarchical clustering in conjunction with Ward's criteria (XXX reference). Hierarchical cluster techniques fuse neighbouring points sequentially to form bigger clusters, beginning with a full pairwise distance matrix. The distance between clusters is described using a "linkage technique". This agglomerative approach successively merges the pair of clusters with the shortest between-cluster distance using Ward's linkage method. Hierarchical algorithms are one of the most widely used, can operate with data of any shape, has reasonable scalability, and the number of clusters is not needed as a parameter.
